Manuscript

### 2018-12-12 manuscript.Rmd
update Rmd
update lineage plots

# Set up

@@

# Functions {.tabset .tabset-fade .tabset-pills}

@@

## Make G2P lineage mutation status plotly
```{r}
MutPlotlyByLineage <- function(lineage_name) {
  use_data <- filter(g2p_druggenelin_all_summ, group_general_lineage_name == lineage_name)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  ticker <- 0

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
  ccle_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ccle_summ) <= 1) {
    ccle_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
    ccle_lin_p_ttest_res <- paste0("t(", round(ccle_lin_p_ttest$parameter, 1), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
  }

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
  ctrp_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ctrp_summ) <= 1) {
    ctrp_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
    ctrp_lin_p_ttest_res <- paste0("t(", round(ctrp_lin_p_ttest$parameter, 1), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
  }

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  gdsc_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
    gdsc_lin_p_ttest_res <- paste0("t(", round(gdsc_lin_p_ttest$parameter, 1), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
  }

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
                          df = c(round(ccle_lin_p_ttest$parameter, 3), round(ctrp_lin_p_ttest$parameter, 3), round(gdsc_lin_p_ttest$parameter, 3)),
                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
                          group_general_lineage_name = lineage_name)
  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "In G2P?", title = toupper(lineage_name)) +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage/", lineage_name, "_mut_plotly.html"))

@@

  mut_plot <- cowplot::plot_grid(plot_box,
                     plot_point,
                     nrow = 2,
                     rel_heights = c(1, 4))
  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage/", lineage_name, "_mut_plot.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")

@@

## Make G2P lineage Pearson plotlys
```{r}
PearsonPlotlyByLineage <- function(lineage) {
  print(paste0("Lineage: ", toupper(lineage)))
  use_data <- filter(signif_lin_g2p_grid, group_general_lineage_name == lineage)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  ticker_ge <- 0
  ticker_cn <- 0
  ticker <- 0

@@

  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + 1)
  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
                          df_GE = c(trunc(ccle_ge_ttest$parameter), trunc(ctrp_ge_ttest$parameter), trunc(gdsc_ge_ttest$parameter)),
                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
                          df_CN = c(trunc(ccle_cn_ttest$parameter), trunc(ctrp_cn_ttest$parameter), trunc(gdsc_cn_ttest$parameter)),
                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
                          group_general_lineage_name = lineage)

  ## Gene expression
  if(sum(!is.na(use_data$Pearson_GE_Abs)) > 0) {
    plot_ge_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text_repel(data = subset(use_data, InG2P == "Yes"), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and gene expression") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_ge_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      labs(x = "In G2P?", title = toupper(lineage)) +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
    plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage/", lineage, "_ge_plotly.html"))
    print("Gene expression plotly: DONE")

@@

    png_ge <- cowplot::plot_grid(png_ge_box, png_ge_point, nrow = 2, rel_heights = c(1, 4))
    png_ge
    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage/", lineage, "_ge_plot.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
    print("Gene expression plot: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plots: None") }

  ## Copy number
  if(sum(!is.na(use_data$Pearson_CN_Abs)) > 0) {
    plot_cn_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_CN_Label, color = InG2P, fill = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text_repel(data = subset(use_data, InG2P == "Yes"), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and copy number") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_cn_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      labs(x = "In G2P?", title = toupper(lineage)) +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
    plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))
    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage/", lineage, "_cn_plotly.html"))
    print("Copy number plotly: DONE")

@@

    png_cn <- cowplot::plot_grid(png_cn_box, png_cn_point, nrow = 2, rel_heights = c(1, 4))
    png_cn
    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage/", lineage, "_cn_plot.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
    print("Copy number plot: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plots: None") }

@@

# Data management {.tabset .tabset-fade .tabset-pills}

@@

## Genomic annotations

### CCLE MAF file

@@

### CCLE copy number file

@@

### CCLE gene expression file

@@

@@

```{r}
length(unique(ccle_data_g2p_grid$Drug))
length(unique(ccle_data_g2p_grid$Drug_Gene))
```

# Mutation Status Wilcoxon tests

@@

@@

### G2P genes

```{r, eval=FALSE}
crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene)
crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
saveRDS(crispr_signif_g2p_gene, "./data_munging/rds/crispr_signif_g2p_gene.rds")
```

@@

## Drug screens: All CRISPR genes

CCLE:

user   system  elapsed 
1483.399  262.649 1901.698

>>>>

# SET UP

@@

# FUNCTIONS {.tabset .tabset-fade .tabset-pills}

@@

## Make lineage mut plots

```{r}
MutPlotsByLineage <- function(lineage_name) {

  use_data <- filter(dgl_mut_grid_summ, group_general_lineage_name == lineage_name)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  ticker <- 0

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_summ <- use_data_ccle %>% count(InG2P)
  ccle_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ccle_summ) <= 1) {
    ccle_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn < 2) { ccle_lin_p_ttest_res <-  NA }
  else if(use_data_ccle_summ[use_data_ccle_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_lin_p_ttest <- t.test(use_data_ccle$p ~ use_data_ccle$InG2P)
    ccle_lin_p_ttest_res <- paste0("t(", trunc(ccle_lin_p_ttest$parameter), ") = ", round(ccle_lin_p_ttest$statistic, 2), ", p = ", round(ccle_lin_p_ttest$p.value, 3))
  }

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_summ <- use_data_ctrp %>% count(InG2P)
  ctrp_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_ctrp_summ) <= 1) {
    ctrp_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn < 2) { ctrp_lin_p_ttest_res <-  NA }
  else if(use_data_ctrp_summ[use_data_ctrp_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_lin_p_ttest <- t.test(use_data_ctrp$p ~ use_data_ctrp$InG2P)
    ctrp_lin_p_ttest_res <- paste0("t(", trunc(ctrp_lin_p_ttest$parameter), ") = ", round(ctrp_lin_p_ttest$statistic, 2), ", p = ", round(ctrp_lin_p_ttest$p.value, 3))
  }

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  gdsc_lin_p_ttest <- data.frame(statistic = NA,
                                 parameter =  NA,
                                 p.value = NA)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_lin_p_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_lin_p_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
    gdsc_lin_p_ttest_res <- paste0("t(", trunc(gdsc_lin_p_ttest$parameter), ") = ", round(gdsc_lin_p_ttest$statistic, 2), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
  }

  y_value <- ifelse(ticker == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)

  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_p = c(ccle_lin_p_ttest_res, ctrp_lin_p_ttest_res, gdsc_lin_p_ttest_res),
                          t_statistic = c(round(ccle_lin_p_ttest$statistic, 3), round(ctrp_lin_p_ttest$statistic, 3), round(gdsc_lin_p_ttest$statistic, 3)),
                          df = c(trunc(ccle_lin_p_ttest$parameter), trunc(ctrp_lin_p_ttest$parameter), trunc(gdsc_lin_p_ttest$parameter)),
                          p_value = c(round(ccle_lin_p_ttest$p.value, 3), round(ctrp_lin_p_ttest$p.value, 3), round(gdsc_lin_p_ttest$p.value, 3)),
                          group_general_lineage_name = lineage_name)
  plot_point <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(xlim = c(0, 1), ylim = c(0, y_value)) +
    scale_x_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    scale_y_continuous(breaks = pretty_breaks()) +
    geom_point(mapping = aes(label = Drug_Gene, color = InG2P, x = p, y = n), alpha = 0.5) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    geom_text_repel(data = subset(use_data, InG2P == "Yes"), mapping = aes(x = p, y = n, label = Drug_Gene), size = 3, segment.size = 0.2, segment.color = "grey50") +
    geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value, label = Test_Results_p), nudge_y = 0.1) +
    labs(x = "Drug-gene association p-value between mutation groups", y = "Number of level A G2P associations") +
    theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
  plot_box <- ggplot(data = use_data) +
    facet_wrap(~ Dataset, drop = FALSE) +
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks = seq(0, 1, by = 0.1), labels = seq(0, 1, by = 0.1)) +
    geom_violin(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.5) +
    geom_boxplot(mapping = aes(color = InG2P, y = p, x = InG2P), alpha = 0.75, width = 0.25) +
    scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
    coord_flip() +
    labs(x = "In G2P?", title = toupper(lineage_name)) +
    theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))
  plot <- subplot(plot_box, plot_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>% layout(title = toupper(lineage_name), margin = list(t = 75, l = 75), xaxis5 = list(title = "Gene-drug association p-value between mutation groups"), yaxis = list(title = "Level A G2P\nassociation", domain = c(0.8, 1)), yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

@@

  mut_plot <- cowplot::plot_grid(plot_box,
                     plot_point,
                     nrow = 2,
                     rel_heights = c(1, 4))

  saveWidgetFix(widget = plot, file = paste0("./plots/manuscript/plotlys_mut_by_lineage_grid/", lineage_name, "_mut_plotly_grid.html"))
  ggsave(paste0("./plots/manuscript/pngs_mut_by_lineage_grid/", lineage_name, "_mut_plot_grid.png"), mut_plot, device = "png", dpi = 450, width = 12, height = 6, units =   "in")

@@

## Make lineage GE/CN plots

```{r}
PearsonPlotsByLineage <- function(lineage) {
  print(paste0("Lineage: ", toupper(lineage)))
  use_data <- filter(dgl_signif_pearson_g2p_grid, group_general_lineage_name == lineage)
  use_data$Dataset <- factor(use_data$Dataset, levels = c("CCLE", "CTRP", "GDSC"))
  use_data$Pearson_GE_Label <- paste0(round(use_data$Pearson_Pval_GE, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  use_data$Pearson_CN_Label <- paste0(round(use_data$Pearson_Pval_CN, 3), "\nDrug_Gene: ", use_data$Drug_Gene)
  ticker_ge <- 0
  ticker_cn <- 0
  ticker <- 0

@@

  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)
  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + max(use_data$n) * 0.1)

  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
                          df_GE = c(trunc(ccle_ge_ttest$parameter), trunc(ctrp_ge_ttest$parameter), trunc(gdsc_ge_ttest$parameter)),
                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
                          df_CN = c(trunc(ccle_cn_ttest$parameter), trunc(ctrp_cn_ttest$parameter), trunc(gdsc_cn_ttest$parameter)),
                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
                          group_general_lineage_name = lineage)

  ## Gene expression
  if(sum(!is.na(use_data$Pearson_GE_Abs)) > 0) {
    plot_ge_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_GE_Label, color = InG2P, fill = InG2P, shape = Pearson_GE_Sign, x = Pearson_GE_Abs, y = n), alpha = 0.5) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text_repel(data = subset(use_data, InG2P == "Yes" & n > 10), aes(label = Drug_Gene, x = Pearson_GE_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_ge, label = Test_Results_GE), nudge_y = 1) +
      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and gene expression") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_ge_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_GE_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      labs(x = "In G2P?", title = toupper(lineage)) +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

    plot_ge <- subplot(plot_ge_box, plot_ge_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and gene expression"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

@@

    png_ge <- cowplot::plot_grid(png_ge_box, png_ge_point, nrow = 2, rel_heights = c(1, 4))
    png_ge

    saveWidgetFix(widget = plot_ge, file = paste0("./plots/manuscript/plotlys_ge_by_lineage_grid/", lineage, "_ge_plotly_grid.html"))
    ggsave(paste0("./plots/manuscript/pngs_ge_by_lineage_grid/", lineage, "_ge_plot_grid.png"), png_ge, device = "png", dpi = 450, width = 12, height = 6, units = "in")
    print("Gene expression plots: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_GE_Abs)) == 0) { print("Gene expression plots: None") }

  ## Copy number
  if(sum(!is.na(use_data$Pearson_CN_Abs)) > 0) {
    plot_cn_point <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      scale_y_continuous(breaks = pretty_breaks()) +
      geom_point(mapping = aes(label = Pearson_CN_Label, color = InG2P, fill = InG2P, shape = Pearson_CN_Sign, x = Pearson_CN_Abs, y = n), alpha = 0.5, position = position_jitter(width = 0, height = 0.15)) +
      scale_shape_manual(values = c(25, 24), labels = c("Negative", "Positive")) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      scale_fill_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      geom_text_repel(data = subset(use_data, InG2P == "Yes"  & n > 10), aes(label = Drug_Gene, x = Pearson_CN_Abs, y = n), size = 3, segment.size = 0.2, segment.color = "grey50") +
      geom_text(data = summ_text, mapping = aes(x = 0.5, y = y_value_cn, label = Test_Results_CN), nudge_y = 1) +
      labs(y = "Number of level A G2P associations", x = "Pearson correlation coefficient between drug-gene AUC and copy number") +
      theme(legend.position = "none", plot.margin = unit(c(0.05, 0.5, 0.5, 0.5), "cm"), strip.background = element_blank(), strip.text.x = element_blank())
    plot_cn_box <- ggplot(data = use_data) +
      facet_wrap(~ Dataset, drop = FALSE) +
      geom_violin(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5) +
      geom_boxplot(mapping = aes(color = InG2P, y = Pearson_CN_Abs, x = InG2P), alpha = 0.5, width = 0.25) +
      scale_color_manual(values = c("Yes" = "darkorchid4", "No" = "lightpink")) +
      coord_flip() +
      labs(x = "In G2P?", title = toupper(lineage)) +
      theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = unit(c(0.5, 0.5, 0.05, 0.5), "cm"))

    plot_cn <- subplot(plot_cn_box, plot_cn_point, nrows = 2, titleX = TRUE, titleY = TRUE) %>%
               layout(title = lineage, margin = list(t = 75, l = 75),
                      xaxis5 = list(title = "Pearson correlation coefficient between drug-gene AUC and copy number"),
                      yaxis = list(title = "In G2P?", domain = c(0.8, 1)),
                      yaxis2 = list(title = "Number of level A G2P associations", domain = c(0, 0.79)))

@@

    png_cn <- cowplot::plot_grid(png_cn_box, png_cn_point, nrow = 2, rel_heights = c(1, 4))
    png_cn

    saveWidgetFix(widget = plot_cn, file = paste0("./plots/manuscript/plotlys_cn_by_lineage_grid/", lineage, "_cn_plotly_grid.html"))
    ggsave(paste0("./plots/manuscript/pngs_cn_by_lineage_grid/", lineage, "_cn_plot_grid.png"), png_cn, device = "png", dpi = 450, width = 12, height = 6, units = "in")
    print("Copy number plots: DONE")
  }
  else if(sum(!is.na(use_data$Pearson_CN_Abs)) == 0) { print("Copy number plots: None") }

@@

# DATA MANAGEMENT {.tabset .tabset-fade .tabset-pills}

@@

## CCLE genomic annotations

### Mutation status (Mut)

@@

### Copy number (CN)

@@

### Gene expression (GE)

@@

### Merge drug data and annotations

### Filter drug data

@@

# WILCOXON TESTS

@@

Wilcoxon tests for assessing effect of mutation status on gene essentiality scores (CRISPR) and AUC (CCLE, CTRP, and GDSC).

@@

Test G2P genes in lineage-agnostic context:
```{r, eval=FALSE}
crispr_signif_g2p_gene <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_g2p, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_g2p_gene <- adj_signif(crispr_signif_g2p_gene)
crispr_signif_g2p_gene <- crispr_signif_g2p_gene[order(crispr_signif_g2p_gene$p),]
saveRDS(crispr_signif_g2p_gene, "./data_munging/rds/crispr_signif_g2p_gene.rds")
```

@@

# PEARSON CORRELATIONS

Pearson correlations for assessing effect of gene expression and copy number on gene essentiality score and AUC.
